DeepPicar:​ ​A​ ​Low-cost​ ​Deep​ ​Neural​ ​Network-based​ ​Autonomous​ ​Car

### 2017-10-04 paper/evaluation.tex
figure position
perf_vs_modelcnt

\begin{figure}[t]
  \centering
  \includegraphics[width=.5\textwidth]{Total_Processing_Time}
  \caption{DeepPicar's control loop processing times over 1000 input image frames.}
  \label{fig:control-loop-timing}
\end{figure}

@@

\subsection{Multimodel Performance}
We also test the capability of the DeepPicar to run multiple models at the same time, and whether each 
model can successfully perform within the given deadline. Specifically, the platform is tested in the 
cases of running 2 and 4 models simultaneously. For each case, all models are allocated an equal number 
of cores. That is, 2 models are given 2 cores each and 4 models are given 1 core each.

\begin{figure}[h]
  \centering
  \includegraphics[width=.5\textwidth]{figs/2ModelChart}
  \caption{ Change in inferencing time when 2 models are run concurrently. }
\end{figure}

>>>>

\begin{figure}[t]
  \centering
  \includegraphics[width=.45\textwidth]{Total_Processing_Time}
  \caption{DeepPicar's control loop processing times over 1000 input image frames.}
  \label{fig:control-loop-timing}
\end{figure}

@@

\subsection{Effect of Co-scheduling Multiple DNN Models}

We also test the capability of the DeepPicar to run multiple models at
the same time, and whether each model can successfully perform within
the given deadline. Specifically, the platform is tested in the cases
of running 2 and 4 models simultaneously. For each case, all models
are allocated an equal number of cores. That is, 2 models are given 2
cores each and 4 models are given 1 core each.

\begin{figure}[h]
  \centering
  \includegraphics[width=.45\textwidth]{figs/perf_vs_modelcnt}
  \caption{Timing impact of co-scheduling multiple DNNs. X-axis shows
    the system configuration: \#of DNN models x \#of CPU cores\/DNN. For
    example, '4x1' means running four DNN models each of which is
    assigned to run on one CPU core, where as '2x2' means running two DNN
    models, each of which is assigned to run on two CPU cores.}
  \label{fig:perf-vs-multimodel}
\end{figure}

%% \begin{figure}[h]
%%   \centering
%%   \includegraphics[width=.5\textwidth]{figs/2ModelChart}
%%   \caption{ Change in inferencing time when 2 models are run concurrently. }
%% \end{figure}
